Methodology for Assessing the State of the Practice for Domain X

### 2020-09-07 StateOfPractice/Methodology/Methodology.tex
copied Empirical Measures into Appendix in Methodology document for the purpose of traceability
updated AHP section of Methodology

\section{Analytic Hierarchy Process} \label{SecAHP}
The analytical hierarchy process (AHP) ranks software packages using pairwise comparisons of quality scores. We have developed a tool for conducting this process. The tool includes an AHP JAR script and a sensitivity analysis JAR script that is used to ensure that the software package rankings are appropriate with respect to the uncertainty of the quality scores.
The README file of the tool is found \href{run:../AHP2020/LBM/README.txt}{here}. This file outlines the requirements for, and configuration and usage of the JAR scripts. The JAR scripts, source code, and required libraries are located in the same folder as the README file.

@@

>>>>

\section{Analytic Hierarchy Process} \label{SecAHP}
The Analytical Hierarchy Process (AHP) is a decision-making technique that can be used when comparing multiple options by multiple criteria. In our work AHP is used for comparing and ranking the software packages of a domain using the quality scores that are gathered in the \href{run:Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}{Measurement Template}. AHP performs a pairwise analysis between each of the quality options using a matrix which is then used to generate an overall score for each software package for the given criteria. \cite{SmithEtAl2016} shows how AHP is applied to ranking software based on quality measures. We have developed a tool for conducting this process. The tool includes an AHP JAR script and a sensitivity analysis JAR script that is used to ensure that the software package rankings are appropriate with respect to the uncertainty of the quality scores. The README file of the tool is found \href{run:../AHP2020/LBM/README.txt}{here}. This file outlines the requirements for, and configuration and usage of, the JAR scripts. The JAR scripts, source code, and required libraries are located in the same folder as the README file.

@@

\subsection{Empirical Measures Considerations - Raw Data}

Measures that can be extracted from on-line repos.

\subsection{Empirical Measures Considerations - Processed Data}
Metrics that can be calculated from the raw data.

\subsection{Empirical Measures Considerations - Tool Tests}
\ad{This section is currently a note of unorganized contents. Most parts will beremoved or relocated.}
